\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-05-31 graph_abs.tex
rearranged sections

\mypara{System under test ($\System$)}

@@

\todo{Add figure? graph-abs -enrich-> pwa-transition-system -bmc->
concrete-CEX}

>>>>

\subsection{System under test ($\System$)}

@@

\begin{figure}[!htbp]
\begin{center}
\tikzstyle{line} = [thick]
\tikzstyle{arw} = [->, thick,>=stealth,shorten <=2pt, shorten >=2pt]
\tikzstyle{block} = [rectangle, minimum width=0.5cm, minimum height=1.0cm, text centered, draw=black, align=center]%, fill=blue!25]
\begin{tikzpicture}[scale=1.0, on grid, auto]

    \node (G) at (-4,0) {$G$};
    \node (GR) at (0,0) {$G^R$};
    \node (CEX) at (4,0) {$CEx$};

    \node (enrich) [block] at (-2, 0) {\scriptsize Enrich using \\ \scriptsize affine maps};
    \node (BMC) [block] at (2, 0) {\scriptsize Find CEx \\ \scriptsize using BMC};

    %\node[align=center] at (0, 0) {\scriptsize Enrich using \\ \scriptsize Regression \\ \scriptsize(OLS)};

    %\draw [line] (-2.0,-0.5) rectangle (-1.0,0.5);
    \draw[arw] (G.east) -- (enrich.west);
    \draw[arw] (enrich.east) -- (GR.west);
    \draw[arw] (GR.east) -- (BMC.west);
    \draw[arw] (BMC.east) -- (CEX.west);

\end{tikzpicture}
\end{center}
\vspace*{-.3cm}
\caption{Finding counter-examples (CEx) in a graph abstraction using PWA models.}
\label{fig:overview}
\vspace*{-.3cm}
\end{figure}
